RandomForest

### 2021-12-05 randomforest.Rmd
Got the forest working

```{r}
rf_fit <- randomForest(HeartDisease ~ ., data = train, mtry = sqrt(ncol(train) - 1), importance = TRUE, type= "classification")

@@

testnmse <- mean((rf-true)^2)

paste("Random forest tree test error",testnmse)
```

>>>>

```{r}
rf_fit <- randomForest(as.factor(HeartDisease) ~ ., data = train, mtry = sqrt(ncol(train) - 1), importance = TRUE, type= "classification")

@@

predicted2 <- ifelse(rf>0.5,1,0)

confm2<-table(predicted=rf,True=true)
confm2

paste("the overall fraction of correct predictions in the test dataset is :",(confm2[1,1]+confm2[2,2])/sum(confm2))
```

```{r}
print(rf_fit)
```

```{r}
plot(rf_fit)
```
